---
title: "x reasons to drink fermented maize"
output: github_document
---

> I am looking for a way to setup potential collaboration with people through content I will be creating on YouTube. This repository is intended to be an open channel for collaborations through my YouTube creations. Find the repository in my Github: [Youtube_Colab](https://github.com/MorgsBrew/Youtube_Colab). Follow me on [Youtube](https://www.youtube.com/channel/UCIby2YRaGNjqEv4mbJ-URlQ?view_as=subscriber) 

***

# Load the libraries

I always start by loading *libraries*. The [tidyverse](https://www.tidyverse.org) is probably the package I use the most. There are other random tools I have found which I know how to apply and like to use.

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(rmarkdown)    # You need this library to run this template.
library(epuRate)      # Install with devtools: install_github("holtzy/epuRate", force=TRUE)
library(BiocStyle)
library(knitcitations)
library(devtools)

# Use this function for installing
#if (!require("devtools")) {
#   install.packages("devtools")
#   library(devtools)
#}
```


```{r bib, message = FALSE, warning = FALSE}
## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'devtools' = citation('devtools'),
    'knitcitations' = citation('knitcitations')
)
```


# Introduction

In this post I am going to get in to the bits and pieces of why I love Mageu. I have decided to use this as my first topic in this new format because it allows for the easy separation of different sections which can then be brought together using a range of tools. 

## Background 

Mageu is a traditional African drink made from rotten (fermented) maize. The drink has strong cultural roots and is enjoyed by millions of South Africans daily. I first encountered the drink when researching various traditional Zulu ferments. I brought this term to Besta (my Zulu Mom) simply asking if she had herd of this stuff called "Ma-gggggggg-ewu". Her response was full of joy because she was about to teach me about this stuff. Way back in 2016 we made our first batch and what a Love story it has been ever since.

## Current Knowlege

My current knowledge of Mageu consists of several discussions with various people over the past three years. To summarize this I would simply say that Mageu is a fermented beverage that has high numbers of bacteria associated with lactic acid fermentation (**Lactobacillus**). There is likely a low percentage of alcohol in mild brews and higher in the stronger (more time and more sugar). The highest I would guess in the average brew would be less than 1 % ABV. Mageu is a good probiotic for people 

## Gaps in the knowledge

The main gaps I would like to close are the specific communities found in Mageu and what is the actual alcoholic content of an average brew? Other things to consider are what the possible impacts of Mageu might be for people with:

  * "Gluten intolerance"
  * IBS
  * Diabetics

## Aims and Objectives

The primary aim of this post is going to be merging some kind of scientific method and knowledge about Mageu into a movie while detailing the process required to make Mageu.

The Objectives are to (1) explain the cultural history of Mageu and the recepie we use, (2) explore its' structure and interactions with the holobiont, (3) interact with it in some scientific way, and (4) create a story in the process

# Materials and methods

## Naming the post

When it comes to naming youtube videos there are certain conventions that work better than others. Some great examples of the most successful searches which seem to be inline with my thingking for this video are:

* Do it yourself (DIY)
* How to ...
* x Reasons why ...
* x Ways to

The most "relevant" naming conventions for this post, after comparisons were made between them and Aims, I have decided to go with "x Reasons why ...". This naming strategy is intended to improve search applicability and enhance the chance of more views.

## Mageu Recipe 

This is made in the same way that Bestas mom showed her. She calls it Zulu Maas

The ingredients are:

- Maize Meal
- Water
- Salt
- Sugar

5 tbs Maize meal are measured out in a medium mixing cup. Some cold water is added and it is mixed using a wooden spoon. At the same time a medium/small pot is filled half full with water and set to boil. When the water is boiling the pre-mix is added while stirring. Some salt is sprinkled into this process at the users desire.

Once the meal is thick, the pot is placed in the sink surrounded by cold water to cool. Once cool the meal is sieved to remove lumps. 5 tbs of sugar are then added to this and stirred in. The beaker is covered and left standing for 1 - 2 days to allow fermentation to begin. Once ready it is put into the fridge where is is consumed like a cold drink or pored over porridge like a Zulu Mass

### Shot list ideas

* Pot boiling
* Sieving the mageu
* Stirring the pot
* Pouring the mageu
* Weighing and measuring
* Mixing the ingredients
* Microscope

## Video audio and editing

* Samsung WB350F
* DJI Mavic Pro
* GoPro Hero 5 Session
* MacBook Pro
* iPhone 5S
* Final Cut Pro X
* Rode Smartlav+ 

## Scientific interaction

### Visual inspection

In an attempt to 'see' the Mageu I will prepare a slide and view it under my dissecting microscope at 16x and 40x magnification. It is unlikely that I will see anything but this is the most I can do for magnification.

### Growth measurments

50 mL centrifuge tubes sealed with balloons will be the culture vessels used to asses basic growth rates under low, medium or high sugar concentrations. 

## Literature sources

Finding peer reviewed scientific literature has completely changed since I first started my Academic path in 2007. I remember when Google Scholar was still taboo and it has now become my main/ only way to interact with the internet. If I encounter any paywalls I will do the responsible thing by colluding with the Russians.

## Tweet analysis

### Hashtag MAGEU usage frequency 

#### Use case over time

In this section someone will have to add some basic tweet analytic which gathers the number of # mentions over the time period 2016 - present. 

  x = time
  y = number of mentions

#### Use case by location

It would be great to have the actual use cases mapped on a world map or just Africa if more relevant.

# Results

## Naming this post

## Mageu recipe

## Scientific "interaction" with Mageu

### Visual inspection

### Growth measuments

## Hashtag (#) Mageu Tweet analysis

### Use case by time

### Use case by location

# Discuassion

# Conclusion

# Acknowledgements


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('devtools')` `r citep(bib[['devtools']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`

# References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

# Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```

